Scheduling and Amortization for MPC

### 2022-02-01 biometric_vectorization_example.tex
Some more notes on arrays, raise_dim and drop_dim.

>>>>

There are three kinds of arrays (for now all kept internally as one-dimensional arrays, but that's under discussion).
\begin{itemize}

\item Scalars: These are scalar variables that we lift into arrays for the purpose of vectorization. 
For those, all writes are canonical writes and all reads are canonical reads. We may apply both raise dimension 
and drop dimension on these.

\item Read-only input arrays: Read-only inputs. There are NO writes while we may have non-canonical reads, $f(i,j,k)$. 
Vectorization will lift the raise dimension operation at the beginning of the function and raise dimension may reshape 
arrays. If there are multiple "views" of the input array, there could be multiple raise dimension statements to create
these views. The invariant is that at reads in loops, the reads of "views" of the original input array will be canonical.
Only raise-dimension applies.

 \item Read-write output arrays: Writes are canonical (by restriction) but reads can be non-canonical. Conjecture:
 do nothing. Dependence analysis takes care of limiting vectorization so non-canonical access will work. 
Still work in progress, but we may apply both raise and drop dimension.

\end{itemize}
